\section{Future Development}
In the scope of the master project the project team has set up an initial game which is executable and testable for various settings including multiple teams per game and the most important administrator features. As the project was accompanied by a project planning tool called ''Trello'', there have been a lot of future tasks which may be implemented in the future but weren't planned within the scope of this Master project. The most epic features will be described in the following paragraph. \\

As not enough data for a bootstrapped game was provided, the authors focused on developing a game which will be played with historical data. The game is easily extendable for this purpose, as the initial plan was to set up both modes. The authors had to revise this plan due to the lack of provided data. When creating a game the administrator can choose the game type which is either a bootstrapped or a historical game. \\

% TODO more epic feature improvements

The projects plan is being set up for a first real game-execution by the Executive education's final seminar which will be held in July 2019. Additionally to the current courses where the application was used (as described in a latter chapter), the Department of Banking and Finance plans to set up another execution for the assessment course ''Banking and Finance II'', in which 700 students would participate in. The effort of setting this up for such a large number of students would need a lot of stress testing for the application.
